---
output:
  word_document: default
  html_document: default
---

```{r}
rm(list = ls())

library(ISLR)
library(class)
library(caret)
library(leaps)
library(corrplot)
library(car)
require(e1071)
library(bootstrap)
library(rpart)
library(gbm)
```

```{r}
white_wine = read.csv2("https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality-white.csv")

summary(white_wine)
```
The white wine dataset contain 12 variables and 4898 observations. The 12 variables are: fixed.acidity, volatile.acidity, citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, density, pH, sulphates, alcohol, quality.
```{r}
white_wine = data.frame(lapply(white_wine, function(x) as.numeric(as.character(x))))

hist(white_wine$quality, main = "Histogram for Quality of White Wine", 
     xlab ="Quality", ylab = "count", col ="seagreen")

```
Quality ranges from 3 to 9 for white wine. It has most values concentrated in the categories 5, 6 and 7. Only a small proportion is in the categories 3,4,8 and 9

```{r}
###################################################################################
# Histogram for all predictors
###################################################################################

par(mfrow = c(3,4))
hist(white_wine$fixed.acidity, main = "Histogram for fixed.acidity", prob = TRUE, xlab = "fixed.acidity", ylab = "count", col = "lightgreen")
lines(density(white_wine$fixed.acidity), lwd = 1.5, col = "black")

hist(white_wine$volatile.acidity, main = "Histogram for volatile.acidity", prob = TRUE, xlab = "volatile.acidity", ylab = "count", col = "lightgreen")
lines(density(white_wine$volatile.acidity), lwd = 1.5, col = "black")

hist(white_wine$citric.acid, main = "Histogram for citric.acid", prob = TRUE,   xlab = "citric.acid", ylab = "count", col = "lightgreen")
lines(density(white_wine$citric.acid), lwd = 1.5, col = "black")

hist(white_wine$residual.sugar, main = "Histogram for residual.sugar", prob = TRUE, xlab = "residual.sugar", ylab = "count", col = "lightgreen")
lines(density(white_wine$residual.sugar), lwd = 1.5, col = "black")

hist(white_wine$chlorides, main = "Histogram for chlorides", prob = TRUE,       xlab = "chlorides", ylab = "count", col = "lightgreen")
lines(density(white_wine$chlorides), lwd = 1.5, col = "black")

hist(white_wine$free.sulfur.dioxide, main = "Histogram for free.sulfur.dioxide", prob = TRUE, xlab = "free.sulfur.dioxide", ylab = "count", col = "lightgreen")
lines(density(white_wine$free.sulfur.dioxide), lwd = 1.5, col = "black")

hist(white_wine$total.sulfur.dioxide, main = "Histogram for total.sulfur.dioxide", prob = TRUE, xlab = "total.sulfur.dioxide", ylab = "count", col = "lightgreen")
lines(density(white_wine$total.sulfur.dioxide), lwd = 1.5, col = "black")

hist(white_wine$density, main = "Histogram for density", prob = TRUE, xlab = "density", ylab = "count", col = "lightgreen")
lines(density(white_wine$density), lwd = 1.5, col = "black")

hist(white_wine$pH, main = "Histogram for pH", prob = TRUE, xlab = "pH", ylab = "count", col = "lightgreen")
lines(density(white_wine$pH), lwd = 1.5, col = "black")

hist(white_wine$sulphates, main = "Histogram for sulphates", prob = TRUE, xlab = "sulphates", ylab = "count", col = "lightgreen")
lines(density(white_wine$sulphates), lwd = 1.5, col = "black")

hist(white_wine$alcohol, main = "Histogram for alcohol", prob = TRUE, xlab = "alcohol", ylab = "count", col = "lightgreen")
lines(density(white_wine$alcohol), lwd = 1.5, col = "black")

```

